Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-14 programlogic.tex
fix defs of ghost maps

  % To do so, we introduce the protocol separating read-only (fragmental) and authorative (full ownership) accesses to the page tables, specifically $\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$. 
  % We realize this protocol by embedding it into an already existing \textsf{Iris}'s ghost-map (or view\_maps) construction
  In Iris this is realized by using an authoritative resource algebra: there is a single \emph{authoritative} global copy of the (ghost)
  map caching virtual-to-physical address translations, and for each entry a read only \emph{partial} ownership of that key-value pair.
  The resource algebra itself is instantiated as:
  \[\mathcal{A}\textsf{bsPTableWalk} \stackrel{\triangle}{=} \textsc{Auth} (\; \mathcal{W}_{64} \;\rightarrow_{\textrm{fin}} \;  (\mathcal{W}_{64} \; \rightarrow_{\textrm{fin}}\;  (\textsc{Frac }, \mathord{+}) \times (\textsc{Agree } \Loc,\mathord{=}) ))\]
We replace the physical
 $\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$
with
fragmental ownership of the ghost-map ($ \sumwalkabs\vaddr\qfrac\paddr$),
 whose ownership just ensures that the virtual address ($\vaddr$) is mapped to a page (referenced by $\paddr$)

@@

\subsection{Address-Space Management}
\label{sec:aspacemanagement}
\todo[inline]{Colin has not looked at this section in detail yet.
It is clear the discussion of the cr3 update needs updating for doubles}
So far, we have introduced logical abstractions for a single address space. However, \textsf{VMM} implementations handle more than one address-space which we abstract as a ghost map from root address of an address-space to a namespace labelling the address space
\[\mathcal{A}\textsf{spaces} \stackrel{\triangle}{=} \textsc{Auth} (\; \mathcal{W}_{64} \;\rightarrow_{\textrm{fin}} \; (\textsc{Agree } \mathsf{GName},\mathord{=}) ) \]

>>>>

  % To do so, we introduce the protocol separating read-only (fragmental) and authorative (full ownership) accesses to the page tables, specifically $\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$. 
  % We realize this protocol by embedding it into an already existing \textsf{Iris}'s ghost-map (or view\_maps) construction
  In Iris this is realized by using an authoritative resource algebra: there is a single \emph{authoritative} global copy of the (ghost)
  map caching virtual-to-physical address translations, and for each entry a read only \emph{partial} ownership of that key-value pair.
  The resource algebra itself is instantiated as:
  \[\mathcal{A}\textsf{bsPTableWalk} \stackrel{\triangle}{=} \textsc{Auth} (\; \mathcal{W}_{64} \;\rightarrow_{\textrm{fin}} \;  ( (\textsc{Frac }, \mathord{+}) \times (\textsc{Agree } \Loc,\mathord{=}) ))\]
We replace the physical
 $\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$
with
fragmental ownership of the ghost-map ($ \sumwalkabs\vaddr\qfrac\paddr$),
 whose ownership just ensures that the virtual address ($\vaddr$) is mapped to a page (referenced by $\paddr$)

@@

\subsection{Address-Space Management}
\label{sec:aspacemanagement}
\todo[inline]{Colin has not looked at this section in detail yet.
It is clear the discussion of the cr3 update needs updating for doubles}
So far, we have introduced logical abstractions for a single address space. However, \textsf{VMM} implementations handle more than one address-space which we abstract as a ghost map from root address of an address-space to a namespace labelling the address space
\[\mathcal{A}\textsf{spaces} \stackrel{\triangle}{=} \textsc{Auth} (\; \mathcal{W}_{64} \;\rightarrow_{\textrm{fin}} \;  ( (\textsc{Frac }, \mathord{+}) \times (\textsc{Agree } \Loc,\mathord{=}) )) \]
